Racial Force Probe

### 2024-02-15 paper/paper.qmd
Graph added

#### Workspace setup ####
# install.packages("tidyverse")
# install.packages("knitr")
# install.packages("here")
# install.packages("ggplot2")
# install.packages("janitor")

library(ggplot2)
library(tidyverse)
library(knitr)
library(here)
library(janitor)
```

@@

```{r}
#| message: false
#| echo: false
#| label: fig-covid
#| fig-cap: Covid trends in the jail
```

>>>>

#### Workspace setup ####
# install.packages("tidyverse")
# install.packages("knitr")
# install.packages("here")
# install.packages("ggplot2")
# install.packages("janitor")
# install.packages("zoo")

library(ggplot2)
library(tidyverse)
library(knitr)
library(here)
library(janitor)
library(zoo)
```

@@

```{r}
#| message: false
#| echo: false
#| label: fig-covid
#| fig-cap: Covid trends in the jail

pop <- c(1217352, 412783, 328239523)  # population denominators

# Read CSV file with the correct date format
x <- read.csv("data/raw_data/covidts01.csv", header = TRUE, stringsAsFactors = FALSE)
x$date <- as.Date(x$date, format = "%m/%d/%Y")  # Specify the correct date format

# Calculate rolling averages
pp <- 1e5 * zoo::rollapply((x$pp_cases[-1] - x$pp_cases[-132]), width = 7, FUN = mean) / pop[1]
sp <- 1e5 * zoo::rollapply((x$sp_cases[-1] - x$sp_cases[-132]), width = 7, FUN = mean) / pop[2]
gp <- 1e5 * zoo::rollapply((x$gp_cases[-1] - x$gp_cases[-132]), width = 7, FUN = mean) / pop[3]

# Combine data into a data frame
ts_data <- data.frame(
  date = rep(x$date[-(1:7)], 3),
  new_cases_per_100k = c(pp, sp, gp),
  group = rep(c("Incarcerated", "Prison Staff", "General Population"), each = length(pp))
)

# Create the figure using ggplot2 with solid lines
ggplot(ts_data, aes(x = date, y = new_cases_per_100k, color = group)) +
  geom_line(size = 0.8) +  # Adjust the line thickness here (e.g., size = 0.8)
  scale_x_date(date_labels = "%B", date_breaks = "1 month", limits = c(min(ts_data$date), max(ts_data$date))) +
  scale_y_continuous(limits = c(0, 150), breaks = seq(0, 150, 25)) +
  labs(x = NULL, y = "New cases per 100,000", title = "Seven-Day Moving Average of New Daily COVID-19 Cases per 100,000 Among
Those in Prison, Prison Staff, and in the General Population: May to September
2020") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(as.Date(c("2020-04-01", "2020-05-01", "2020-06-01", "2020-07-01", "2020-08-01", "2020-09-01"))),
             linetype = "dashed", color = "gray") +
  annotate("text", x = as.Date(c("2020-04-01", "2020-05-01", "2020-06-01", "2020-07-01", "2020-08-01", "2020-09-01")),
           y = 150, label = c("April 2020", "May 2020", "June 2020", "July 2020", "August 2020", "September 2020"),
           vjust = -0.5, hjust = 0, color = "gray") +
  scale_color_manual(values = c("blue", "red", "green"))
